### 2024-09-16 Response_V0.1/Response.tex

	\begin{my}{1cm}{1cm}
	\rev{\,\,\,\, In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL (MADRL), which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption.

	\,\,\,\, In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.

\,\,\,\, In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.

\,\,\,\, In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, thus a more realistic MEC scenario is needed. Besides the works \cite{huang2019deep}--\cite{liao2023online}, Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a MARL method to minimize both energy consumption and processing delay. Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DDQN-based algorithm.
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs.

\,\,\,\, While studies like \cite{wu2023computation}--\cite{zhao2019deep} explored task offloading problems in a more advanced scenario and proposed some DRL-based algorithms, MEC systems often encounter challenges related to managing time-varying resource requests from heterogeneous devices, imposing significant challenges in resource accessibility and overall system performance. To address this issue, the authors applied queuing theory to model MEC systems more accurately, reflecting real-world scenarios. 
In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.}
\end{my}

\vspace{6mm}

We have also revised the motivation and contributions subsection, as below.

\vspace{6mm}

	\begin{my}{1cm}{1cm}
	\rev{\,\,\,\, Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  \textcolor{blue}{As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. 
    While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.} In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands.}
\end{my}

@@

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``Some sota methods (e.g., DDQN, DDPG) are expected to be compared in the section on performance evaluation, and authors should have more discussions about the evaluation results rather than merely introducing them. Besides, I think it is better to design the evaluations with a real dataset. Besides, 9\% and 6\% are not significant improvements compared to other methods.''} \newline

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``Other concerns are also expected to be addressed: \textcolor{purple}{(a) be careful to use words like "battery level" to express the energy consumption, because some of the energy is provided by the wired line power. (b) Most of the references are out of 3 years, please investigate more studies published in recent years.} (c) The authors should thoroughly check the writing style, grammar, and spelling to enhance the paper's clarity, conciseness, and overall impact.''} \newline

\underline{Authors' Reply}: (a) We have changed the word "battry level" to "energy state" in whole paper. \newline

(b) We have added some related refrences, which are under 3 years, in Section I, as follow: \newline

		\begin{my}{1cm}{1cm}
	\rev{
		{\small
			\noindent\hspace{-0.3mm}\cite{munir2021multi} Munir, Md Shirajum and Tran, Nguyen H and Saad, Walid and Hong, Choong Seon, ``Multi-agent meta-reinforcement learning for self-powered and sustainable edge computing systems,'' \textit{IEEE Trans. Netw. Serv. Manag.}, vol. 18, no. 3, pp. 3353-3374. 2021.\\[6pt]
			\cite{wu2024combining} G. Wu, X. Chen, Y. Shen, Z. Xu, H. Zhang, S. Shen, and S. Yu,``Combining Lyapunov optimization with Actor-Critic networks for privacy-aware IIoT computation offloading,'' in \textit{IEEE Internet Things J.}, 2024, Early Access\\[6pt]
			\cite{lin2022multi} Lin, Shih-Yang and Huang, Chung-Ming and Wu, Tzu-Yu, ``Multi-access edge computing-based vehicle-vehicle-RSU data offloading over the multi-RSU-overlapped environment,'' \textit{IEEE Open J. Intell. Transp. Syst.}, vol. 3, pp. 7--32, 2022.\\[6pt]
			\cite{wei2023many} Wei, Zhiwei and Li, Bing and Zhang, Rongqing and Cheng, Xiang and Yang, Liuqing, ``Many-to-many task offloading in vehicular fog computing: A multi-agent deep reinforcement learning approach,'' \textit{IEEE Trans. Mob. Comput.}, vol. 23, no. 3, pp. 2107--2122, 2023.\\[6pt]
			\cite{wu2023multi} G. Wu, Z. Xu, H. Zhang, S. Shen, and S. Yu,  ``Multi-agent DRL for joint completion delay and energy consumption with queuing theory in MEC-based IIoT,'' in \textit{Journal of Parallel and Distributed Computing}, vol. 176, pp. 80–94, Jun. 2023.\\[6pt]
			\cite{wu2023computation} G. Wu, H. Wang, H. Zhang, Y. Zhao, S. Yu, and S. Shen, ``Computation offloading method using stochastic games for software-defined-network-based multiagent mobile edge computing,'' \textit{IEEE Internet Things J.}, vol. 10, no. 20, pp. 17620–17634, Oct. 2023.\\[6pt]
			\cite{wu2024privacy} G. Wu, X. Chen, Z. Gao, H. Zhang, S. Yu, and S. Shen, ``Privacy-preserving offloading scheme in multi-access mobile edge computing based on MADRL,'' \textit{Journal of Parallel and Distributed Computing}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[6pt]
			\cite{yuan2023adaptive} Yuan, Shijing and Dong, Beiyu and Lvy, Hongtao and Liu, Hongze and Chen, Hongyang and Wu, Chentao and Guo, Song and Ding, Yue and Li, Jie, ``Adaptive incentivize for cross-silo federated learning in IIoT: A multi-agent reinforcement learning approach,'' \textit{IEEE Internet Things J.}, 2023.\\[6pt]
			\cite{zhang2023multi} Zhang, Jing and Shen, Fei and Tang, Liang and Yan, Feng and Qin, Fei and Wang, Chao, ``A Multi-Agent Reinforcement Learning Approach for Dynamic Offloading with Partial Information-Sharing in IoT Networks,'' \textit{2023 IEEE 98th Vehicular Technology Conference (VTC2023-Fall)}, pp. 1--5, 2023.\\[6pt]
			\cite{tang2022uav} Tang, Qiang and Liu, Lixin and Jin, Caiyan and Wang, Jin and Liao, Zhuofan and Luo, Yuansheng, ``An UAV-assisted mobile edge computing offloading strategy for minimizing energy consumption,'' \textit{Computer Networks}, vol. 207, pp. 108857, 2022.\\[6pt]
			\cite{seo2022differential} Seo, Hyeonseok and Oh, Hyeontaek and Choi, Jun Kyun and Park, Sangdon, ``Differential pricing-based task offloading for delay-sensitive IoT applications in mobile edge computing system,'' \textit{IEEE Internet Things J.}, vol. 9, no. 19, pp. 19116--19131, 2022.\\[6pt]
			\cite{guo2022energy} Guo, Mian and Li, Qirui and Peng, Zhiping and Liu, Xiushan and Cui, Delong, ``Energy harvesting computation offloading game towards minimizing delay for mobile edge computing,'' \textit{Computer Networks}, vol. 204, pp. 108678, 2022.\\[6pt]
			\cite{li2022joint} Li, Yuwei and Yang, Bo and Wu, Hao and Han, Qiaoni and Chen, Cailian and Guan, Xinping, ``Joint offloading decision and resource allocation for vehicular fog-edge computing networks: A contract-stackelberg approach,'' \textit{IEEE Internet Things J.}, vol. 9, no. 17, pp. 15969--15982, 2022.\\[10pt]}\\}
\end{my}

@@

\end{enumerate}

\newpage

\section{Response to Reviewer 2}
\begin{enumerate}

	\item \underline{Reviewer's Comment}: 
	\textit{``\textcolor{purple}{The authors should provide a comparative table to highlight their contributions. Specially, the authors should compare their method with other references on computation task offloading cited in the paper, including aspects such as scenarios, methods, advances, drawbacks, and so on.''}} \newline

	\underline{Authors' Reply}: To address the reviewer's comment, we have added a table comparing the characteristics of related works in the related works subsection, as below:
	\begin{table*}[htbp]\textcolor{blue}{
			\renewcommand{\arraystretch}{0.6}
			\captionsetup{name=TABLE}
			\caption{Comparison of Related Works Characteristic\vspace{4mm}}
			\scalebox{0.7}{%
				\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3cm}p{4.6cm}l} 
					\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
					\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
					\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
					\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
					\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
					\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
					\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
					\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & Not consider tasks with maximum delay tolerance\\\midrule
					\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
					\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
					\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
					\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
					\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & Not take user's deman into consideration \\\midrule
					\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
					\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
					\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
					QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table1}}
	\end{table*}
	\item \underline{Reviewer's Comment}: 
	\textit{``I think more explanations should be added for the QoE function. How can the defined function reflect QoE?''} \newline

	\underline{Authors' Reply}:

	\item \underline{Reviewer's Comment}: 
	\textit{``\textcolor{purple}{(a) What inputs and outputs of Algorithm 2? (b) They should be added to make readers clearly understand the results.''}} \\\newline
	\underline{Authors' Reply}: (a) To address the reviewer concern about algorithm 2, we have revised secound paragraph of subsection (Training Process Algorithm at EN $j \in \mathcal{J})$ in Section IV to clarify the inputs and outputs of algorithms 2, as follows. \newline

@@

	We have also revised algorithm 1 and 2, as below.\\

\begin{my}{0.5cm}{0.5cm}	
\rev{\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Training Process)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{\textcolor{blue}{Input:}}} \renewcommand{\algorithmicensure}{\textbf{\textcolor{blue}{Output:}}} \Require \textcolor{blue}{experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}$} \Ensure \textcolor{blue}{parameter vector $\theta_i^{\text{E}}$} 
	\end{algorithmic} 
\end{algorithm} 
\end{minipage}
\vspace{5mm}

### 2024-09-16 Response_V0.1/Response.tex

\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Offloading Decision)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{Input:}} \renewcommand{\algorithmicensure}{\textbf{Output:}}\Require state space $\mathcal{S}$, action space $\mathcal{A}$
			\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{blue}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
		\end{algorithmic} 
	\end{algorithm} 
\end{minipage}}
\end{my}

\vspace{10mm}
	\item \underline{Reviewer's Comment}: 
	\textit{``\textcolor{purple}{The authors should open their experiments in github, so that other researchers can compare their work with other ones.''}} \newline
	\underline{Authors' Reply}: To address the reviewer comment, we make our experiments more accessible by sharing our GitHub rerepository. We have added it into the end of first paragraph of Section V, as follows.
	\begin{my}{1cm}{1cm}
		\rev{Detailed settings regarding the neural networks and simulation can be found at our github repository. }
	\end{my}
	We have also provided repository URL link in the footnote of Page 8 as below.
	\begin{my}{1cm}{1cm}
		\rev{The code for reproducing the simulation results of this letter is available at\newline https://github.com/ImanRHT/QECO.} \newline
	\end{my}

	\item \underline{Reviewer's Comment}: 
	\textit{``\textcolor{purple}{The following references closely related to the current work should be discussed or compared with the current work for completeness.''}} \newline
		\begin{my}{1cm}{1cm}
		\rev{
			{\small
				\noindent\hspace{-0.5mm}\cite{wu2023multi} G. Wu, Z. Xu, H. Zhang, S. Shen, and S. Yu,  ``Multi-agent DRL for joint completion delay and energy consumption with queuing theory in MEC-based IIoT,'' in \textit{Journal of Parallel and Distributed Computing}, vol. 176, pp. 80–94, Jun. 2023.\\[6pt]
				\cite{wu2023computation} G. Wu, H. Wang, H. Zhang, Y. Zhao, S. Yu, and S. Shen, ``Computation offloading method using stochastic games for software-defined-network-based multiagent mobile edge computing,'' \textit{IEEE Internet of Things Journal}, vol. 10, no. 20, pp. 17620–17634, Oct. 2023.\\[6pt]
				\cite{wu2024privacy} G. Wu, X. Chen, Z. Gao, H. Zhang, S. Yu, and S. Shen, ``Privacy-preserving offloading scheme in multi-access mobile edge computing based on MADRL,'' \textit{Journal of Parallel and Distributed Computing}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[6pt]
				\cite{wu2024combining} G. Wu, X. Chen, Y. Shen, Z. Xu, H. Zhang, S. Shen, and S. Yu,``Combining Lyapunov optimization with Actor-Critic networks for privacy-aware IIoT computation offloading,'' in \textit{IEEE Internet of Things Journal}, 2024, Early Access\\[10pt]}\\}
	\end{my}

@@

	\item \underline{Reviewer's Comment}: 
	\textit{``\textcolor{purple}{The following references closely related to the current work should be discussed or compared with the current work for completeness.''}} \newline
		\begin{my}{1cm}{1cm}
		\rev{
			{\small
				\noindent\hspace{-0.5mm}\cite{wu2023multi} G. Wu, Z. Xu, H. Zhang, S. Shen, and S. Yu,  ``Multi-agent DRL for joint completion delay and energy consumption with queuing theory in MEC-based IIoT,'' in \textit{Journal of Parallel and Distributed Computing}, vol. 176, pp. 80–94, Jun. 2023.\\[6pt]
				\cite{wu2023computation} G. Wu, H. Wang, H. Zhang, Y. Zhao, S. Yu, and S. Shen, ``Computation offloading method using stochastic games for software-defined-network-based multiagent mobile edge computing,'' \textit{IEEE Internet of Things Journal}, vol. 10, no. 20, pp. 17620–17634, Oct. 2023.\\[6pt]
				\cite{wu2024privacy} G. Wu, X. Chen, Z. Gao, H. Zhang, S. Yu, and S. Shen, ``Privacy-preserving offloading scheme in multi-access mobile edge computing based on MADRL,'' \textit{Journal of Parallel and Distributed Computing}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[6pt]
				\cite{wu2024combining} G. Wu, X. Chen, Y. Shen, Z. Xu, H. Zhang, S. Shen, and S. Yu,``Combining Lyapunov optimization with Actor-Critic networks for privacy-aware IIoT computation offloading,'' in \textit{IEEE Internet of Things Journal}, 2024, Early Access\\[10pt]}\\}
	\end{my}

	\underline{Authors' Reply}:\\

	We have cited these works in the Section I of the revised manuscript.\\
